---
title: "Missing Data"
authors: "Andrey Koval & Jamie Knight"
date: "June 15, 2016"
output: html_document
---  
<!-- for more options study http://rmarkdown.rstudio.com/html_document_format.html  -->
<!-- The report is produced from
REPOSITORY: MAP
BRANCH: the-name-of-the-branch
PATH: ../Reports/
-->

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of only one directory.-->
```{r, echo=F, message=F} 
library(knitr)
opts_knit$set(root.dir='../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external script file. -->
```{r, echo=F, message=T}
require(knitr)
opts_chunk$set(
  results='show', # Set
  message = TRUE, # De
  comment = NA,   #   fau
  tidy = FALSE,   #     lts
#   fig.height = 4.8, # physical dimensions
#   fig.width = 6.5,  # of produced impage
  out.width = NULL, # how it looks in html document
  fig.path = 'figure_rmd/', # where images from this report are stored
  dev = "png",
  dpi = 100 # resolution: dots per inch. Use 100 to develop, 300-400 to print. adjust
)
C_echo <- TRUE
C_message<- FALSE
C_warning<- FALSE

options(width=120) #So the output is 50% wider than the default.
read_chunk("./reports/missing-data.R") # the file to which knitr calls for the chunks
```

##Intro
Missing Pattern using MAP data.
Skip right to the bottom on the page and look at the very last dynamic table.

You can sort the missing pattern by clicking on the arrow.
You can also select how many you would like to view. The default it currently set to 10.

```{r Intro, message=C_message, warning=C_warning}
```

##Load Packages

If you would like to look at all the code details are below with how to code this using dplyr
```{r LoadPackages, message=C_message, warning=C_warning}
```


```{r LoadData, echo=TRUE, message=C_message, warning=C_warning}
```

##Code
Using the dplyr package in R.

In the dynamic tables below you can sort the missing patter by clicking on the arrow.
You can also select how many you would like to view. The default it currently set to 10.

```{r Table, echo=TRUE, message=C_message, warning=C_warning}
```



